Blocking-resistant communication\\through domain fronting

### 2015-01-10 docs/meek.tex
Can observe overhead from CDN invoices.
Need to update overhead estimates for #12778.
Do the xspace thing.

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek\ combines
\vp{What is the point of the backslash-space after \meek here?  The
backslace-xspace already takes care of the trailing whitespace.}
fronting with an HTTP-based tunneling proxy
that decodes a sequence of HTTP requests and feeds their contents into Tor.
A censor sees only a sequence of HTTPS requests to an allowed domain.
We describe our experience with deploying \meek.
% \meek, or something based on it,
% has been adopted by other circumvention systems including
% [blinded for anonymous submission].
% ANON
% Lantern and Psiphon.

@@

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a pluggable transport~\cite{pt} for Tor.
\meek\ combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received by the server from Tor
are returned to the client within HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

@@

\meek\ has been built into an experimental release of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront
as intermediate web service backends.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:survey} names other fronting-capable services
and Section~\ref{sec:discussion} describes other possible deployments.
\vp{It's confusing here having out-of-order references to sections.  This
also occurs below}
In addition to the Tor pluggable transport,
systems based on \meek\ are now used by other circumvention systems including
[blinded for anonymous submission].
% ANON
% including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek\ is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

Domain fronting and HTTPS address two major circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
Our goal is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than domain blacklists or deep packet inspection---to
force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to traffic analysis
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek\
to samples of HTTPS traffic at a network router.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each JavaScript-based proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek\ uses just a few high-value front domains on hard-to-block network infrastructure.
A drawback with flash proxy's use of the browser is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek\ in its use of
domain fronting with App Engine.
\vp{Was it literally an inspiration, or was it concurrent development?
I thought it was more the latter.}
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent does not use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload
\vp{``generally'' upload---what's their practical alternative?}
their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014,
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek\ over App Engine was similarly affected.
\vp{Add mention of what \meek\ platforms still worked.}
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
% ANON
% Psiphon uses domain fronting based on \meek\ as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
% ANON
% Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
\vp{Explain Pisphon's relevance to meek}

@@

We show the components of the system in Figure~\ref{fig:architecture}.
The parts that are new in \meek\
are the programs \meekclient and \meekserver,
\vp{It would help to use a different typeface for \meekserver, etc.}
which are \meek's interface with Tor.

@@

When \meek\ is used with Google App Engine, one other component is needed:
a small ``reflector'' web app that simply copies any request
it receives and forwards it to a remote instance of \meekserver.
App Engine cannot
\vp{explain why it can't}
directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards requests
when the response is not already cached.

The main technical challenge of the protocol is splitting a TCP stream up
into a sequence of HTTP requests and responses.
The body of each HTTP request and response carries
a small chunk of upstream or downstream communication.
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order, and without gaps or duplicates.
\meek\ takes a naive approach: requests and responses are strictly serialized.
The client does not send a second chunk of data
(i.e., make another HTTPS request) until it has
received the response to its first.
The reconstructed stream is simply the concatenation
of bodies in the order they arrive.
Handling stream reconstruction this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
Section~\ref{sec:discussion} discusses a more efficient encoding
that would enable multiple requests in parallel.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek\ HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and \mbox{X-Session-Id} headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek\ uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send,
simply to give the server an opportunity to send something back.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.  \vp{Do you jitter the polling?}
% ANON
% The other technique,
% implemented in Psiphon's version of \meek,
The other technique
uses streaming HTTP responses over persistent HTTP connections.
\vp{It would help to have a timing diagram to illustrate this.}
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response stream it has open to that client and starts a new one.
This second technique is especially beneficial for bulk downloads,
but does not work on all services:
notably Google App Engine does not support this kind of streaming.

@@

\begin{center}
\begin{tabular}{r@{}r l}
          &    514 & Tor cell \\
          &  $+$29 & Tor TLS record \\
$\approx$ & $+$400 & \meek\ HTTP header \\
$\approx$ &  $+$50 & \meek\ TLS record \\
\hline
$\approx$ &   1000 & total
\end{tabular}
\end{center}
\vp{Not clear this table is worth the real estate}

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field in the header and the specifics of the intermediate web service's TLS configuration,
but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
\vp{It might be helpful to have a table showing upload/download size/efficiency}
Streaming HTTP responses, when they are possible, reduce overhead further,
% ANON
% Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is needed for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle,
so they do not affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

@@

The TLS handshake is largely plaintext~\cite[\S7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on their handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} in Appendix~\ref{sec:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome}
show two browsers which have TLS fingerprints different from Go's
and different from each other's.
A censor could block an uncamouflaged \meek\ using Go's TLS fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

The use of a browser extension brings benefits beyond TLS camouflage.
It means \meek's HTTP tunnel inherits other characteristics of the browser:
for instance
how often it resolves DNS,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when \meek\ is used with Tor Browser
because Tor Browser
is a modified version of Firefox:
we can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (headless Firefox),
saving space in distribution packages
and sparing the user the chore of having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when \meek\ is activated and deactivated.

@@

\vp{This whole section should be beefed up with a deeper assessment.  Along
these lines, it would help to include a summary table.}
This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek\
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically requires an investment of time and money.

@@

CloudFlare~\cite{cloudflare}
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be a popular one
(causing high collateral damage if blocked),
or the censor may simply block it entirely.
It is doubly bad when a domain is blocked in this way,
because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that does not send SNI.
\vp{Would be quite valuable to more broadly assess the viability
of using domainless fronting}
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek\ does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

One of our goals in developing \meek\ is to force
the censor to use relatively more expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek\ is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
\vp{sketch for the reader why it's resistant to active probing}
We hope to force the censor to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

% Advantage is that we are probably proxying web traffic.
As \meek\ is based on HTTPS,
we compare traffic traces of \meek\ against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek\ in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek\ trace is 687~MB
and spans 4.5~hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from 
%Lawrence Berkeley National Laboratory (\lbl)
a large ($\approx$~4K~users)
research lab [blinded as \lbl for anonymous submission],
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The \lbl trace consists 313~MB of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we analyzed the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek\ on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the \lbl traffic trace,
and \meek\ running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

@@

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek\
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it is difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google's traffic is different than Akamai's.

>>>>

We have implemented domain fronting in a system called \meek,
a pluggable transport for Tor.
\meek combines
fronting with an HTTP-based tunneling proxy
that decodes a sequence of HTTP requests and feeds their contents into Tor.
A censor sees only a sequence of HTTPS requests to an allowed domain.
We describe our experience with deploying \meek.
% \meek, or something based on it,
% has been adopted by other circumvention systems including
% [blinded for anonymous submission].
% ANON
% Lantern and Psiphon.

@@

We have developed domain fronting into a full-fledged circumvention system called \meek,
implemented as a pluggable transport~\cite{pt} for Tor.
\meek combines fronting with an HTTP-based tunneling proxy:
upstream data are transformed into a sequence of HTTP requests,
which are fronted in order to reach a proxy server.
The server decodes the requests and feeds their payloads
into the Tor network.
Downstream data received by the server from Tor
are returned to the client within HTTP responses.
\meek's architecture appears in Figure~\ref{fig:architecture}.
Section~\ref{sec:architecture} describes how it works in detail.

@@

\meek has been built into an experimental release of Tor Browser,
and has a small number of users.
Our deployment so far uses Google App Engine and Amazon CloudFront
as intermediate web service backends.
% with the hidden actual domain \urll{meek-reflect.appspot.com}
% hidden by the front \urll{www.google.com}.
Section~\ref{sec:survey} names other fronting-capable services
and Section~\ref{sec:discussion} describes other possible deployments.
\vp{It's confusing here having out-of-order references to sections.  This
also occurs below}
In addition to the Tor pluggable transport,
systems based on \meek are now used by other circumvention systems including
[blinded for anonymous submission].
% ANON
% including Psiphon~\cite{psiphon} and Lantern~\cite{lantern}.

% \meek is designed to have features attractive in a circumvention transport.
% It is easy to use, not requiring the configuration of any bridge addresses.
% In Tor Browser, users need only select ``meek''
% from a pulldown menu in order to use it.
% It resists blocking by address and by content,
% Section~\ref{sec:discussion}

Domain fronting and HTTPS address two major circumvention challenges,
those of hiding the destination and of obscuring the contents of a message.
There remain other, more subtle, attributes of communication
that could serve as a basis for blocking.
For example, the plaintext handshake is a fingerprintable part of TLS.
Section~\ref{sec:browserextension} describes how we use a web browser extension as an instrument for making HTTPS requests,
to make \meek's TLS and HTTPS characteristics
match those of a browser as closely as possible.
Our goal is to force the censor
to employ more sophisticated, expensive, and error-prone statistical tests
to classify traffic as allowed or prohibited,
rather than domain blacklists or deep packet inspection---to
force the practice of censorship to exist in a world
not of simple packet filters,
but of probabilities and false positives.
A preliminary analysis of \meek's resistance to traffic analysis
appears in Section~\ref{sec:trafficanalysis}.
The analysis is based on comparing traffic traces of \meek
to samples of HTTPS traffic at a network router.

@@

Flash proxy~\cite{flashproxy} resists address blocking by
conscripting web users as temporary proxies.
Each JavaScript-based proxy lasts only as long as a
user stays on a web page, so the pool of proxies is constantly changing.
If one of them is blocked, there is soon another to replace it.
Flash proxy's approach to address blocking is in a sense
the opposite of \meek's:
where flash proxy uses many cheap, disposable, individually blockable proxies,
\meek uses just a few high-value front domains on hard-to-block network infrastructure.
A drawback with flash proxy's use of the browser is that
the client must be able to receive a TCP connection; in particular it
must not be behind network address translation~(NAT), which limits flash proxy's usefulness.
Part of the flash proxy protocol requires the client to send
a small amount of unblockable data in a process called rendezvous.
The default rendezvous mechanism has used domain fronting through App Engine since 2013~\cite{flashproxy-reg-appspot}.
Flash proxy itself does nothing to defend against DPI.
Connections between censored clients and browser-based proxies use
WebSocket, a meta-protocol running on HTTP,
but inside the WebSocket framing is the ordinary Tor protocol.
% There exists a prototype transport that attempts to get both
% content-based and address-based blocking resistance by obfuscating traffic
% with obfsproxy before sending it through flash proxy~\cite{obfs-flash}.
% However it is limited because it is not
% possible to obfuscate the outermost WebSocket layer;
% the censor could decide simply to block all WebSocket.

@@

GoAgent~\cite{goagent} is a direct inspiration for \meek in its use of
domain fronting with App Engine.
\vp{Was it literally an inspiration, or was it concurrent development?
I thought it was more the latter.}
Traffic is fronted by the Google frontend server,
using the ``domainless'' fronting model without SNI,
and delivered to its destination by a specialized app running on App Engine.
GoAgent does not use an additional general-purpose proxy after fronting;
rather, HTTP and HTTPS URLs are fetched directly from the App Engine servers.
Because of that, GoAgent is limited to carrying HTTP and HTTPS traffic only,
and the contents of all communications are revealed to Google.
Users of GoAgent generally upload
\vp{``generally'' upload---what's their practical alternative?}
their own personal copy of the proxy code to App Engine,
which is free of charge to use as long as they do not exceed a bandwidth quota.
According to a May 2013 survey~\cite{collateral-freedom},
GoAgent was the circumvention tool most used in
China, with 35\% of survey respondents having used it in the previous month.
This figure is higher than that of paid~(29\%) and free VPNs~(18\%), and far
above that of other special-purpose tools like Tor~(2.9\%) and Psiphon~(2.5\%).
Use of GoAgent in China was disrupted starting in the beginning of June~2014,
when all Google services (including GoAgent's front domains) were blocked~\cite{cn-google-block}.
\meek over App Engine was similarly affected.
\vp{Add mention of what \meek platforms still worked.}
% Users identified reliability, speed, and ease of installation as the most important features of a circumvention tool.

@@

Psiphon~\cite{psiphon} is a network of many one-hop proxies,
with encryption and traffic obfuscation between client and server.
% ANON
% Psiphon uses domain fronting based on \meek as one of its blocking defenses since June~2014~\cite{psiphon-meek-merge}.
Lantern~\cite{lantern} uses a network of proxies running on volunteer computers;
proxy addresses are shared only with trusted friends in order to make them difficult to enumerate.
% ANON
% Lantern~1.4 is planned to use domain fronting inspired by \meek~\cite{lantern-1.3.1}.
\vp{Explain Pisphon's relevance to meek}

@@

We show the components of the system in Figure~\ref{fig:architecture}.
The parts that are new in \meek
are the programs \meekclient and \meekserver,
\vp{It would help to use a different typeface for \meekserver, etc.}
which are \meek's interface with Tor.

@@

When \meek is used with Google App Engine, one other component is needed:
a small ``reflector'' web app that simply copies any request
it receives and forwards it to a remote instance of \meekserver.
App Engine cannot
\vp{explain why it can't}
directly run a Tor bridge,
so we bounce the requests to somewhere that can.
The reflector app emulates the behavior of an origin-pull CDN,
which also simply copies and forwards requests
when the response is not already cached.

The main technical challenge of the protocol is splitting a TCP stream up
into a sequence of HTTP requests and responses.
The body of each HTTP request and response carries
a small chunk of upstream or downstream communication.
There must therefore be some way of making sure that chunks
are correctly reassembled at the other end,
in order, and without gaps or duplicates.
\meek takes a naive approach: requests and responses are strictly serialized.
The client does not send a second chunk of data
(i.e., make another HTTPS request) until it has
received the response to its first.
The reconstructed stream is simply the concatenation
of bodies in the order they arrive.
Handling stream reconstruction this way is simple and guarantees correctness,
but has performance drawbacks because there is a full round-trip
between every send.
Section~\ref{sec:discussion} discusses a more efficient encoding
that would enable multiple requests in parallel.

@@

\x14\x03\x03\x00\x01\x01\x16\x03\x03\x00\x40\x06\x84...
\end{verbatim}
\end{quote}
\caption{
Requests and responses in the \meek HTTP protocol.
The session ID is randomly generated by the client.
Request/response bodies contain successive chunks of a Tor TLS stream
(\texttt{\textbackslash{}x16\textbackslash{}x03\textbackslash{}x01\textbackslash{}x02}
is the beginning of a TLS ClientHello message).
The second POST request is an empty polling request.
The messages shown here is encrypted inside HTTPS until after
it has been fronted,
so the censor cannot use the
Host and \mbox{X-Session-Id} headers for classification.
}
\label{fig:protocol}
\end{figure}

@@

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
\meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send,
simply to give the server an opportunity to send something back.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.  \vp{Do you jitter the polling?}
% ANON
% The other technique,
% implemented in Psiphon's version of \meek,
The other technique
uses streaming HTTP responses over persistent HTTP connections.
\vp{It would help to have a timing diagram to illustrate this.}
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response stream it has open to that client and starts a new one.
This second technique is especially beneficial for bulk downloads,
but does not work on all services:
notably Google App Engine does not support this kind of streaming.

@@

% These numbers have changed since https://trac.torproject.org/projects/tor/ticket/12778.
\begin{center}
\begin{tabular}{r@{}r l}
          &    514 & Tor cell \\
          &  $+$29 & Tor TLS record \\
$\approx$ & $+$400 & \meek HTTP header \\
$\approx$ &  $+$50 & \meek TLS record \\
\hline
$\approx$ &   1000 & total
\end{tabular}
\end{center}
\vp{Not clear this table is worth the real estate}

% >>> (1*543+450.)/(1*543)
% 1.828729281767956
% >>> (2*543+450.)/(2*543)
% 1.4143646408839778
% >>> (3*543+450.)/(3*543)
% 1.276243093922652
\noindent
The total overhead varies according to the length
of the Host field in the header and the specifics of the intermediate web service's TLS configuration,
but is somewhere in the neighborhood of $(543+450)/543-1\approx83$\%.
This is the worst case, when Tor sends a single cell.
Tor can bunch multiple cells into one transmission;
if two cells are sent at once, the overhead drops to
${\approx}41$\%; if three, it is ${\approx}28$\%.
Bulk uploads and downloads tend to have less overhead, bunching many cells at once.
% We can tell exactly how much overhead exists in practice by looking at our CDN invoices.
% According to https://lists.torproject.org/pipermail/tor-dev/2014-December/007916.html,
% In November 2014 meek-amazon had 167M requests and 1269 GB, or 8153 bytes per request.
% If each request header is 500 bytes, that's about 6%.
\vp{It might be helpful to have a table showing upload/download size/efficiency}
Streaming HTTP responses, when they are possible, reduce overhead further,
% ANON
% Persistent HTTP connections as used by Psiphon reduce overhead further,
because only one HTTP header is needed for a large number of transmissions.
Empty polling requests also use bandwidth,
but they are sent only when the connection is idle,
so they do not affect upload or download speed.
As is discussed in Section~\ref{sec:trafficanalysis},
\meekclient reuses the same TLS connection for many requests,
so the fixed overhead of the initial TLS handshake is amortized.

@@

The TLS handshake is largely plaintext~\cite[\S7.4]{rfc5246}, and leaves
enough room for variation, for example in
the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}
based on their handshake.
(We are only concerned with fingerprinting the client,
because the server's TLS
comes from the intermediate web service;
i.e., it is what you would expect to see when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.
Figure~\ref{fig:ciphersuites} in Appendix~\ref{sec:ciphersuites} shows examples of how TLS client
implementations may detectably differ.
\meekclient is written in the Go programming language,
which has a custom TLS library~\cite{golang-crypto/tls};
Figure~\ref{fig:ciphersuites:golang}
shows how it would appear on the network with no TLS camouflage.
Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome}
show two browsers which have TLS fingerprints different from Go's
and different from each other's.
A censor could block an uncamouflaged \meek using Go's TLS fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

@@

The use of a browser extension brings benefits beyond TLS camouflage.
It means \meek's HTTP tunnel inherits other characteristics of the browser:
for instance
how often it resolves DNS,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when \meek is used with Tor Browser
because Tor Browser
is a modified version of Firefox:
we can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (headless Firefox),
saving space in distribution packages
and sparing the user the chore of having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when \meek is activated and deactivated.

@@

\vp{This whole section should be beefed up with a deeper assessment.  Along
these lines, it would help to include a summary table.}
This section contains a brief survey of fronting-capable
web services we have found, each with its pros and cons.
The list is not exhaustive and is meant to illustrate the broad
support for fronting that exists.
Of the services listed, we have so far deployed \meek
only on Google App Engine and Amazon CloudFront.
For the others, we have only checked that fronting works.
Recall that even web services that support fronting
will front only for their own customers,
so new each deployment typically requires an investment of time and money.

@@

CloudFlare~\cite{cloudflare}
is a CDN also marketed as protection against
denial-of-service attacks.
It appears that any domain name on CloudFlare
can front for any other, even custom user-selected domains;
however it is not obvious which one is best to use as a front.
The front domain needs to be a popular one
(causing high collateral damage if blocked),
or the censor may simply block it entirely.
It is doubly bad when a domain is blocked in this way,
because not only is circumvention foiled,
but some unsuspecting third party has just had their web site blocked.
A solution may be to round-robin through
a pool of popular domain names;
or to use ``domainless'' fronting that does not send SNI.
\vp{Would be quite valuable to more broadly assess the viability
of using domainless fronting}
% Though CloudFlare supports domain fronting,
% its terms of service~\cite{cloudflare-terms}
% seem to prohibit the kind of tunneled proxying that \meek does:
% \begin{quote}
% \textsc{Section 10: Limitation on non-HTML caching}\\
% You acknowledge that CloudFlare's Service is offered as a platform to cache and
% serve web pages and websites and is not offered for other purposes
% \ldots\ you understand and agree to use the Service solely
% for the purpose of hosting and serving web pages\ldots
% \end{quote}

@@

One of our goals in developing \meek is to force
the censor to use relatively more expensive statistical classifiers
to effect blocking---generally, to increase the cost of censorship.
We believe \meek is resistant to the ``easy''
forms of blocking, namely IP address and DNS blocking,
simple pattern-based DPI,
and active probing.
\vp{sketch for the reader why it's resistant to active probing}
We hope to force the censor to resort to measuring
more subtle features of the communication.
In this section we provide a preliminary analysis
of \meek's resistance to such attacks.
Specifically, we consider three traffic features:
packet length distribution,
number of simultaneous connections,
and connection lifetime.

@@

% Advantage is that we are probably proxying web traffic.
As \meek is based on HTTPS,
we compare traffic traces of \meek against
traces of ``ordinary'' HTTPS traffic.
We did a packet capture
of automatically browsing the home pages
of the top 500 Alexa web sites using \meek in Tor Browser,
with the browser camouflage described in Section~\ref{sec:browserextension},
and Google App Engine as the intermediate web service.
The \meek trace is 687~MB
and spans 4.5~hours of network activity.
Our representative of ordinary HTTPS traffic
is a sanitized 10-minute trace
from 
%Lawrence Berkeley National Laboratory (\lbl)
a large ($\approx$~4K~users)
research lab [blinded as \lbl for anonymous submission],
comprising data to and from TCP port 443 on any Google server.
% Mention the non-google if it appears in a figure.
The \lbl trace consists 313~MB of packet headers,
not payloads, destined for TCP port 443 on any Google server.
The original IP addresses were masked by being
replaced by a counter before we analyzed the trace.

\begin{figure}
\centering
\includegraphics[width=\linewidth]{datalen.pdf}
% Output of datalen.R.
%
% LBL
%          0       1430       1418         41       1416       1460       1260
% 0.37665361 0.09120402 0.08493944 0.06090732 0.03101247 0.02941974 0.02021770
%       1400       1359         33
% 0.01673740 0.01126137 0.01100281
%
% meek
%        1418           0        1460         396         196        1024
% 0.405280243 0.376703906 0.071561089 0.019905460 0.018484996 0.014868083
%         811         783         151        1263
% 0.012312668 0.007811963 0.007031241 0.006569205
\begin{tabular}{r r >{\qquad} r r}
\multicolumn{2}{c}{\lbl Google HTTPS} & \multicolumn{2}{>{\qquad}c}{\meek on App Engine} \\
0 bytes & 37.6\% & 1418 bytes & 40.5\% \\
1430 bytes & 9.1\% & 0 bytes & 37.7\% \\
1418 bytes & 8.5\% & 1460 bytes & 7.2\% \\
41 bytes & 6.1\% & 396 bytes & 2.0\% \\
1416 bytes & 3.1\% & 196 bytes & 1.8\% \\
1460 bytes & 2.9\% & 1024 bytes & 1.5\%
\end{tabular}
\caption{
Comparison of TCP payload length distributions
between ordinary HTTPS connections to Google services
from the \lbl traffic trace,
and \meek running on App Engine, fronted through www.google.com.
% The histogram's bin width is 5~bytes.
}
\label{fig:datalen}
\end{figure}

@@

So far we do not find any obvious traffic characteristics that can be useful to reliably distinguish \meek
from other HTTPS traffic.
The long-lived connections and few common packet sizes are
potential targets for a more concerted attack.
The fundamental problem we face is essentially that of steganography,
the need to make our traffic fit some model of ``normal'' traffic.
The problem is inherently difficult,
because it is difficult to say just what normal traffic \emph{is}.
It depends on the network environment;
it also depends on the endpoint.
Google's traffic is different than Akamai's.
